ODGI: scalable tools for pangenome graphs

### 2021-05-31 manuscript/main.tex
Remove table - we'll do this in text

    \begin{table}[!t]
        \processtable{A selection of the tools available in ODGI
        \label{tab:01}} {
            \begin{tabular}{@{}ll@{}}
                \toprule Name & Description \\
                \midrule
                row1          & row1        \\
                row2          & row2        \\
                row3          & row3        \\
                row4          & row4        \\
                \botrule
            \end{tabular}}

@@

    \vspace*{+12pt}
    \textit{Financial Support}: none declared.

@@

    \section*{Data availability}

    Data used to build Human pangenome graphs is available at \href{https://github.com/human-pangenomics/HPP_Year1_Data_Freeze_v1.0}{https://github.com/human-pangenomics/HPP\_Year1\_Data\_Freeze\_v1.0}.

    \section*{Acknowledgements}
    %ToDo
    XXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX.

    \section*{Funding}
    %ToDo
    This work has been supported by the XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX.

>>>>

@@

    % \vspace*{+12pt}
    % \textit{Financial Support}: none declared.

@@

    % \section*{Data availability}

    % Data used to build Human pangenome graphs is available at \href{https://github.com/human-pangenomics/HPP_Year1_Data_Freeze_v1.0}{https://github.com/human-pangenomics/HPP\_Year1\_Data\_Freeze\_v1.0}.

    % \section*{Acknowledgements}
    %ToDo
    % XXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX.

    % \section*{Funding}
    %ToDo
    % This work has been supported by the XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX XXXXXXXX.
